Brief Announcement: An Improved Lower Bound for Dynamic Balanced Graph Partitioning

### 2020-02-15 paper/paper.tex
minireview

We assume OPT begins with the initial configuration
$P_I = I_1, \dots, I_{\ell}$ and moves to the final partition
$P_F = F_1, \dots, F_{\ell}$.
 The \emph{distance} of a configuration $P = C_1, \dots, C_{\ell}$ from the initial configuration is the number of nodes in $P$ that do not reside in their initial cluster.
    That is,
    $\mathit{dist}(P, P_I) := \sum_{j=1}^{\ell} | C_j \setminus I_j |$. 
In other words,
at least $\mathit{dist}(P, P_I)/2$ node swaps are required in order to reach the configuration $P$ from $P_I$.
Therefore,
$\OPT \geq \Delta:= dist(P_F, P_I) $.
 With each re-partitioning,
  PPL moves to a configuration that minimizes distance to the initial configuration $P_I$.
As a result,
ON never ends up in a configuration that is more than $\Delta$ away from $P_I$.
This invariant ensures that ON does not pay too much while reaching $P_F$.

@@

\begin{theorem}	\label{thm:upperbound}
    PPL reaches the final configuration $P_F$ and it is $(2\cdot k\cdot\ell)$-competitive.
\end{theorem}
\begin{proof}
      On each inter-cluster request,
     the algorithm enumerates all $\ell$-way partitions of components
     that are in the same (closest) distance of $P_I$.
     That is, 
     once it reaches a configuration $P$ at distance $\Delta = \mathit{dist} (P, P_I)$,
     it does not move to a configuration
     $P', \mathit{dist} (P', P_I) > \Delta$,
     before it enumerates all configurations at distance $\Delta$.
     Therefore,
     PPL eventually reaches $\Delta=\OPT$ and the configuration $P_F$.
%    including the request that completes revealing of all components that are collocated in $P_F$.
    There are at most $(k-1)\cdot\ell < k\cdot\ell $ calls   to $\mathit{re\mhyphen partition}$
     (i.e., the number of internal edges in $P_F$).
    By Lemma \ref{lemma:rebalancecost},
    each re-partition costs at most $2\cdot\OPT$.
    The total cost is therefore at most $2\cdot\OPT\cdot k\cdot\ell$ which implies the competitive ratio.
%    \mahmoud{This is the cost of moving and the cost of remote comm. is not counted.
%    	So it is 4-competitive (?)}
 \end{proof}

\section{Corollary and Future Directions}

The gap between upper and lower bound is still substantial, as the best known algorithm is the component-respecting algorithm of   \cite{repartition-disc} with competitive ratio $O(k^2\cdot\ell^2)$.

@@

@@

\todo{Check grammar}

>>>>

We assume OPT begins with the initial configuration
$P_I = I_1, \dots, I_{\ell}$ and moves to the final partition
$P_F = F_1, \dots, F_{\ell}$.
 The \emph{distance} of a configuration $P = C_1, \dots, C_{\ell}$ from the initial configuration is the number of nodes in $P$ that do not reside in their initial cluster.
    That is,
    $\mathit{dist}(P, P_I) := \sum_{j=1}^{\ell} | C_j \setminus I_j |$. 
In other words,
at least $\mathit{dist}(P, P_I)/2$ node swaps are required in order to reach the configuration $P$ from $P_I$, and thus
$\OPT \geq \Delta:= dist(P_F, P_I) $.
 With each re-partitioning\maciek{Use consistently: repartition or re-partition. IDK which one is better.},
  PPL moves to a configuration that minimizes distance to the initial configuration $P_I$.
As a result,
ON never ends up in a configuration that is more than $\Delta$ away from $P_I$.
This invariant ensures that ON does not pay too much while reaching $P_F$.

@@

\begin{theorem}	\label{thm:upperbound}
    PPL reaches the final configuration $P_F$ and it is $(2\cdot k\cdot\ell)$-competitive.
\end{theorem}
\begin{proof}
      On each inter-cluster request,
     the algorithm enumerates all $\ell$-way partitions of components
     that are in the same (closest) distance of $P_I$.
     That is, 
     once it reaches a configuration $P$ at distance $\Delta = \mathit{dist} (P, P_I)$,
     it does not move to a configuration
     $P', \mathit{dist} (P', P_I) > \Delta$,
     before it enumerates all configurations at distance $\Delta$.
     Therefore,
     PPL eventually reaches $\Delta=\OPT$ and the configuration $P_F$.
%    including the request that completes revealing of all components that are collocated in $P_F$.
    There are at most $(k-1)\cdot\ell < k\cdot\ell $ calls   to $\mathit{re\mhyphen partition}$
     (i.e., the number of internal edges in $P_F$).
    By Lemma \ref{lemma:rebalancecost},
    each re-partition costs at most $2\cdot\OPT$.
    The total cost is therefore at most $2\cdot\OPT\cdot k\cdot\ell$, which implies the competitive ratio.
%    \mahmoud{This is the cost of moving and the cost of remote comm. is not counted.
%    	So it is 4-competitive (?)}
 \end{proof}

% \section{Corollary and Future Directions}

% The gap between upper and lower bound is still substantial, as the best known algorithm is the component-respecting algorithm of   \cite{repartition-disc} with competitive ratio $O(k^2\cdot\ell^2)$.

@@

\section{Ommited proofs}

@@

\todo{Spellcheck, grammar (grammarly?)}
